SMT-Boosted Security Types for Low-Level MPC

### 2025-11-12 toplas26/metaty.tex
checkpoint

@@

>>>>

When typing functions, a practical programming detail is where the
share type environment precondition $\notg{\Gamma_1}$ is defined.
In our implementation, we write these as an additional component
of \ttt{precondition} annotations, as illustrated in extended
examples discussed in Section \ref{section-examples}.

@@

\subsubsection{Soundness of $\metaprot$ Type Checking}
